\LARGE \bf The Battle for Filter Supremacy: A Retrospective: The Movie: The Game: The Paper

### 2014-12-29 Report/project_report.tex
Quick commit before taking off. Added a few words to plot captions.

Monkey Style Chinese Kung Fu

@@

    \caption{Effect of nullspace projection on MSCKF performance}
    \label{fig:nullspace}
\end{figure}

@@

\subsection{Interval 1: Many visible features}
In the first experiment, we compared the SWF and MSCKF for various parameter settings on an interval with many visible features.
Figure \ref{fig:nVisible_int1} shows the number of visible features in the first interval.
At least three features are visible in $64\%$ of this interval, and the number of visible features is frequently in excess of ten.

@@

    \caption{Comparison of MSCKF, SWF, and IMU integration for multiple parameter settings on the dataset interval $k\in[500,1000]$. The numbers next to ``MSCKF'' in the legend refer to the minimum and maximum feature tracks lengths before an EKF update is triggered, while the number next to ``SWF'' refers to the number of states in the sliding window.}
    \label{fig:comp_1}
\end{figure}

\subsection{Interval 2: Fewer visible features}
In the second experiment, we compared the SWF and MSCKF for various parameter settings on an interval with few visible features.
Figure \ref{fig:nVisible_int2} shows the number of visible features in the second interval.
At least three features are visible in only $56\%$ of this interval, and the number of visible features rarely exceeds ten.
Moreover, the features that are visible do not remain in view of the camera for as long a time as in the first interval.

@@

    \caption{Comparison of MSCKF, SWF, and IMU integration for multiple parameter settings on the dataset interval $k\in[1215,1715]$. The numbers next to ``MSCKF'' in the legend refer to the minimum and maximum feature tracks lengths before an EKF update is triggered, while the number next to ``SWF'' refers to the number of states in the sliding window.}
    \label{fig:comp_2}
\end{figure}

>>>>

Monkey Style Chinese Kung Fu vs. SWFfer Wet Jet

@@

    \caption{Effect of nullspace projection on MSCKF performance. The correlation between the measurement error and the state causes the filter to behave very poorly after a small number of time steps.}
    \label{fig:nullspace}
\end{figure}

@@

\subsection{Experiment 1: Many visible features}
In the first experiment, we compared the SWF and MSCKF for various parameter settings on an interval with many visible features.
Figure \ref{fig:nVisible_int1} shows the number of visible features in the first interval.
At least three features are visible in $64\%$ of this interval, and the number of visible features is frequently in excess of ten.

@@

    \caption{Comparison of MSCKF, SWF, and IMU integration for multiple parameter settings on the dataset interval $k\in[500,1000]$. The numbers next to ``MSCKF'' in the legend refer to the minimum and maximum feature track lengths before an EKF update is triggered, while the number next to ``SWF'' refers to the number of states in the sliding window.}
    \label{fig:comp_1}
\end{figure}

\subsection{Experiment 2: Fewer visible features}
In the second experiment, we compared the SWF and MSCKF for various parameter settings on an interval with few visible features.
Figure \ref{fig:nVisible_int2} shows the number of visible features in the second interval.
At least three features are visible in only $56\%$ of this interval, and the number of visible features rarely exceeds ten.
Moreover, the features that are visible do not remain in view of the camera for as long a time as in the first interval.

@@

    \caption{Comparison of MSCKF, SWF, and IMU integration for multiple parameter settings on the dataset interval $k\in[1215,1715]$. The numbers next to ``MSCKF'' in the legend refer to the minimum and maximum feature track lengths before an EKF update is triggered, while the number next to ``SWF'' refers to the number of states in the sliding window.}
    \label{fig:comp_2}
\end{figure}
